Learning Network Size while Training with ShrinkNets

### 2018-02-08 paper/ICML/introduction.tex
edits

In summary, our contributions are as follows: 
\begin{itemize}
\item we propose a novel technique based on dynamically swiching on and off neurons, 
which allows us to optimize the network size as the network is trained. 
\item we show that our technique is a relaxation\mpv{?} of group sparsity and 
prove \mpv{fill in}. 
\item \srm{Some claim about model size vs performance}
\item we demonstrate the efficacy of our technique on both convolutional and fully-connected neural nets,
showing that 
ShrinkNets finds networks within +/-X\% of best hand-crafted accuracy in XX\% of
training time compared to existing hyperparameter optimization methods.
\item we also demonstrate that ShrinkNets can achieve this accuracy with only YY\% 
of neurons.
\item \srm{Some claim about inference time?}
\item \srm{Some claim about compatibility with existing compression techniques?}
\end{itemize}

>>>>

In summary, our contributions are as follows: 
\begin{compactenum}
\item We propose a novel technique based on dynamically swiching on and off neurons, 
which allows us to optimize the network size as the network is trained. 
\item We show that our technique is a relaxation\mpv{?} of group sparsity and 
prove \mpv{fill in}. 
\item \srm{Some claim about model size vs performance}
\item We demonstrate the efficacy of our technique on both convolutional and fully-connected neural nets,
showing that 
ShrinkNets finds networks within +/-X\% of best hand-crafted accuracy in XX\% of
training time compared to existing hyperparameter optimization methods.
\item We also demonstrate that ShrinkNets can achieve this accuracy with only YY\% 
of neurons.
\item \srm{Some claim about inference time?}
\item \srm{Some claim about compatibility with existing compression techniques?}
\end{compactenum}
